Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-16 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

    \begin{frame}{Cooperative Game Theory}
      \begin{itemize}
         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
         \begin{itemize}
            \item A set of tasks needs to be performed, they require different expertise.
            \item Agents do not have enough resource on their own to perform a task.
            \item Find complementary agents to perform the tasks.
            \begin{itemize}
                \item robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
                \item transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
            \end{itemize}
        \end{itemize}
        \item \textbf{issues:}
            \begin{itemize}
                \item What coalition to form?
                \item How to reward each each member when a task is completed?
            \end{itemize}
      \end{itemize}
    \end{frame}

@@

    \begin{itemize}
        \item \textbf{problem:} a game $(N,v)$, and we assume all agents in $N$ want to cooperate.
        \item \textbf{solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Solution Concepts: Core}
    The core relates to the stability of the grand coalition: \\ No group of agents has any incentive to change coalition.
    \begin{definition}[$Core$ of a game $(N,v)$]\label{dfn:core}
        Let $(N,v)$ be a cooperative game, and assume they form the coalition $N$. The core of $(N,v)$ is the set:
        \vspace{0.1cm}
        \begin{center}
            $Core(N,v) = \{x \in R^n | x$ is a group rational imputation$\}$
        \end{center}
        Equivalently,
        \vspace{0.1cm}
        \begin{center}
            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C) \forall C \subseteq N\}$
        \end{center}
    \end{definition}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.
        \item A convex game has a non-empty core
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Task distribution}
    \begin{itemize}
        \item Our model uses a slightly modified $weighted fair queuing$ method for task distribution rather than Contract-Net.
        \item All the input flow is multiplexed amount different web services with weights proportional to their throughput value ($Th_{ws}$).
        \item Queues will happen if $R_C$ is more than summation web services throughput.
        \item Weighted task rate of: $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ or $Th_{ws}$
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/community.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community Revenue}
    \begin{itemize}
        \item Maximum potential output of a community:
            \begin{equation*}
                PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
            \end{equation*}
        \item if $Th_{ws} > R_C$, the community cannot perform at its maximum potential.
        \item Actual output:
            \begin{equation}\label{out_c}
                Out(C) = \left\{
                  \begin{array}{l l}
                    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
                    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
                  \end{array} \right.
            \end{equation}
    \end{itemize}
\end{frame}

@@

    \begin{itemize}
        \item Approximation of the optimum result for each level, is it possible?
    \end{itemize}

@@

\begin{frame}{Representation and Complexity issues}
    \begin{itemize}
        \item Core and Shapley value are combinatorial problems.
        \item Input size is exponential.
        \item Compact or succinct representation of coalition games. A representation so that the input size is a polynomial in the number of agents.
    \end{itemize}
\end{frame}

    \begin{itemize}
        \item Our web service community valuation function representation ($v(C) = out(C)$) space requirement, grows linearly to input size.
    \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research Activities Goal}
\begin{frame}{Research Activities Goal}
    \begin{itemize}
        \item Analyzing other cooperative solution concepts such as Kernel
        and Nucleolus where payoff division is guaranteed to exist and may
        have optimal results.

@@

        \item Developing an approximation algorithm for shapely value
        payoff distribution vector in community setting.

@@

        %\item Developing an open source, Java based Tool, with UI for
        %solving Core and Shapely solution concepts based on different
        %input valuation functions.
    \end{itemize}
\end{frame}

>>>>

    \begin{frame}{Cooperative Game Theory}
      \begin{itemize}
         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
         \begin{itemize}
            \item A set of tasks needs to be performed, they require different expertise.
            \item Agents do not have enough resource on their own to perform a task.
            \item Find complementary agents to perform the tasks.
            \begin{itemize}
                \item robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
                \item transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
            \end{itemize}
        \end{itemize}
        \item \textbf{Issues:}
            \begin{itemize}
                \item What coalition to form?
                \item How to reward each each member when a task is completed?
            \end{itemize}
      \end{itemize}
    \end{frame}

@@

    \begin{itemize}
        \item \textbf{Problem:} a game $(N,v)$, and we assume all agents in $N$ want to cooperate.
        \item \textbf{Solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Solution Concepts: Core}
    The core relates to the stability of the grand coalition: \\ No group of agents has any incentive to change coalition.
    \begin{definition}[$Core$ of a game $(N,v)$]\label{dfn:core}
        Let $(N,v)$ be a cooperative game, and assume they form the coalition $N$. The core of $(N,v)$ is the set:
        \vspace{0.1cm}
        \begin{center}
            $Core(N,v) = \{x \in R^n | x$ is a group rational imputation$\}$
        \end{center}
        Equivalently,
        \vspace{0.1cm}
        \begin{center}
            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C), \forall C \subseteq N\}$
        \end{center}
    \end{definition}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.
        \item A convex game has a non-empty core
        \item Core and Shapley value are combinatorial problems.
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Task distribution}
    \begin{itemize}
        \item Our model uses a slightly modified \emph{weighted fair queuing} method for task distribution rather than Contract-Net.
        \item All the input flow is multiplexed amount different web services with weights proportional to their throughput value ($Th_{ws}$).
        \item Queues will happen if $R_C$ is more than summation web services throughput.
        \item Weighted task rate of: $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ or $Th_{ws}$
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/community.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community Revenue}
    \begin{itemize}
        \item Maximum potential output of a community:
            \begin{equation*}
                PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
            \end{equation*}
        \item if $\sum_{ws}{Th_{ws}} > R_C$, the community cannot perform at its maximum potential.
        \item Actual output:
            \begin{equation}\label{out_c}
                Out(C) = \left\{
                  \begin{array}{l l}
                    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
                    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
                  \end{array} \right.
            \end{equation}
    \end{itemize}
\end{frame}

@@

    %\begin{itemize}
    %    \item Approximation of the optimum result for each level, is it possible?
    %\end{itemize}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research Activities Goal}
\begin{frame}{Research Activities Goal}
    \begin{enumerate}
        \item Analyzing other cooperative solution concepts such as Kernel
        and Nucleolus where payoff division is guaranteed to exist and may
        have optimal results.

@@

@@

        %\item Developing an open source, Java based Tool, with UI for
        %solving Core and Shapely solution concepts based on different
        %input valuation functions.
    \end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Representation and Complexity issues}
    \begin{itemize}
        \item Core and Shapley value are combinatorial problems.
        \item Input size is exponential.
        \item Compact or succinct representation of coalition games. A representation so that the input size is a polynomial in the number of agents.
    \end{itemize}
\end{frame}

    \begin{itemize}
        \item Our web service community valuation function representation ($v(C) = out(C)$) space requirement, grows linearly to input size.
        \item Developing an approximation algorithm for shapely value payoff distribution vector in community setting.
    \end{itemize}
